Determinism, Complexity, and Predictability in Computer Performance

### 2014-03-13 results.tex
update predictions plot
update caption a bit

Figure~\ref{fig:wpe_vs_mase_all} shows WPE vs. MASE plots for all 360
experiments.
\begin{figure}
  \centering
    \includegraphics[width=\columnwidth]{figs/ARIMA_prediction_vs_entropy}
    \includegraphics[width=\columnwidth]{figs/ARIMA_prediction_vs_entropy}
    \includegraphics[width=\columnwidth]{figs/LMA_prediction_vs_entropy}
\caption{WPE vs. MASE for all trials, methods, and systems.  \svdone,
  \svdthree, and \svdfive are omitted from the top plot for scale
  reasons; their MASE scores are $2.676 \pm 4.328$, $31.386 \pm
  0.282$, and $20.870 \pm 0.192$ respectively.  {\color{red}Replace
    the top plot with a plot of the naive results---but running from 0
    to 3.1 on the horizontal axis and excluding SVD 1, 3, and 5}.  The
  dashed line is the same as in the previous figure [[Ryan, is this
      correct?]].  Numerical values, including means and standard
  deviations of the errors, can be found in Table~\ref{tab:error} in
  the appendix.
% 
%  [[All traces except those from \svd$_1$ lie above the line,
%      indicating that LMA is better suited prediction method for the
%      computer traces considered.]]  [[This comes {\bf long} before the
%      associated discussion in the text, and it's not what this figure
%      is trying to show here.]]
% 
}
    \label{fig:wpe_vs_mase_all}
\end{figure} 
There are 15 points in each cluster, one for each trial.  (The points
in Figure~\ref{fig:wpe_vs_mase_best} are the leftmost of the points
for the corresponding system in any of these three plots.)  The WPE
values do not vary very much across trials.  For most traces, the
variance in MASE scores is low as well, resulting in small, tight
clusters.  In some cases---ARIMA predictions of {\tt col\_major}, for
instance---the MASE variance is larger, which spreads out the clusters
horizontally.  The distribution of the cluster {\sl positions} is
quite different in the three plots: clusters of predictions generated
with the nonlinear LMA method are closer to the dashed line, whereas
the naive and ARIMA prediction clusters are more spread out [[need to
    revisit this wording when get the third image]].  This is a
geometric validation of the second conjecture in this paper, as
described in the following paragraphs.

>>>>

Figure~\ref{fig:wpe_vs_mase_all} shows WPE vs. MASE plots for all 360
experiments.
\begin{figure}
  \centering
%    \includegraphics[width=\columnwidth]{figs/ARIMA_prediction_vs_entropy}
%    \includegraphics[width=\columnwidth]{figs/ARIMA_prediction_vs_entropy}
%    \includegraphics[width=\columnwidth]{figs/LMA_prediction_vs_entropy}
  \includegraphics[width=\columnwidth]{figs/predictions_vs_entropy}
\caption{WPE vs. MASE for all trials, methods, and systems. \svdone, \svdthree, and \svdfive are omitted from the top plot for scale reasons; their MASE scores are $2.676 \pm 4.328$, $31.386 \pm 0.282$, and $20.870 \pm 0.192$ respectively. The dashed line is the same as in the previous figure. Numerical values, including means and standard deviations of the errors, can be found in Table~\ref{tab:error} in the appendix.
% 
%  [[All traces except those from \svd$_1$ lie above the line,
%      indicating that LMA is better suited prediction method for the
%      computer traces considered.]]  [[This comes {\bf long} before the
%      associated discussion in the text, and it's not what this figure
%      is trying to show here.]]
% 
}
    \label{fig:wpe_vs_mase_all}
\end{figure} 
There are 15 points in each cluster, one for each trial.  (The points
in Figure~\ref{fig:wpe_vs_mase_best} are the leftmost of the points
for the corresponding system in any of these three plots.)  The WPE
values do not vary very much across trials.  For most traces, the
variance in MASE scores is low as well, resulting in small, tight
clusters.  In some cases---ARIMA predictions of {\tt col\_major}, for
instance---the MASE variance is larger, which spreads out the clusters
horizontally.  The distribution of the cluster {\sl positions} is
quite different in the three plots: clusters of predictions generated
with the nonlinear LMA method are closer to the dashed line, whereas
the naive and ARIMA prediction clusters are more spread out [[need to
    revisit this wording when get the third image]].  This is a
geometric validation of the second conjecture in this paper, as
described in the following paragraphs.
